### 2023-11-09 manuscript/manuscript.Rmd
Add the term tandem MS
Replace 'LC-MS techniques' with 'LC-MS derived data'

Metabolite annotation is a crucial aspect for ensuring that biological interpretation is possible from metabolomics data sets.
A number of strategies can be employed to annotate peaks in mass spectra.
These can include simple approaches such as heuristic filtering of molecular formulas generated from *m/z* or direct matching putative ionisation products (IPs) to metabolite databases [@draper2009; @green2015; @kind2007];
but also ensemble approaches that integrate a number of strategies like correlation analysis, ionisation product scoring and biotransformations [@baran2013; @fernandez2014; @kuhl2012; @uppal2017].
Tandem MS can also be employed for LC-MS approaches and provides a convenient method for structural validation [@neumann2010].
However, this is unsuitable for metabolome fingerprinting-based techniques due to the presence of structural isomers and isobaric compounds.
Many of the available software packages implementing these strategies are suitable for LC-MS techniques only.

>>>>

Metabolite annotation is a crucial aspect for ensuring that biological interpretation is possible from metabolomics data sets.
A number of strategies can be employed to annotate peaks in mass spectra.
These can include simple approaches such as heuristic filtering of molecular formulas generated from *m/z* or direct matching putative ionisation products (IPs) to metabolite databases [@draper2009; @green2015; @kind2007];
but also ensemble approaches that integrate a number of strategies like correlation analysis, ionisation product scoring and biotransformations [@baran2013; @fernandez2014; @kuhl2012; @uppal2017].
Tandem MS can also be employed for LC-MS approaches and provides a convenient method for structural validation [@neumann2010].
However, tandem MS is unsuitable for metabolome fingerprinting-based techniques due to the presence of structural isomers and isobaric compounds.
Many of the available software packages implementing the strategies outlined above are suitable for LC-MS derived data only.
